### 2017-07-26 paper/evaluation.tex
minor changes

This experiment evaluates the impact of making available to the build
system a growing number of CPUs for testing.  For that reason, we used
a machine with more cores compared to the one described in
Section~\ref{sec:setup}.  We used a Xeon E5-2660v2 (2.20GHz) Intel
processor machine with 80 virtual CPUs (40 cores with two native
threads each) and 256GB of memory, running Ubuntu 14.04 LTS Trusty
Tahr (64-bit version). This experiment uses configuration \emph{\ForkSeq{}}
as the goal is to evaluate the impact on runtime of spawning a growing number of
JVMs in different CPUs.  We selected subject
\subjectScalability{} in this experiment as it represents the case of a long-running test
suite (see Figure~\ref{tab:speedup}) with test cases distributed
across many test classes (194 test classes for \subjectScalability{}).
Note that a test class is the smallest unit that can be used to spawn
a test job on a JVM and that we have no control over which test
classes will be assigned to which JVM that the build system forks.

%\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth
\begin{figure}[h]
    \centering
    \includegraphics[width=.35\textwidth]{R/scalability/scalability.pdf}
    \caption{\label{fig:scalability}Scalability.}
\end{figure}

@@

It is worth mentioning that we used JUnit as opposed to Maven to run
configurations \emph{C*}.  After carefully verifying library versions
for compatibility issues and comparing results with JUnit's we
observed that several of Maven's executions exposed problems.  For
example, Maven incorrectly counts the number of test cases executed
for some cases where test flakiness are observed.  These issues are
categorized and documented on our website~\cite{ourwebpage} with
Docker containers (for reproduction).  To address those issues we
implemented basic JUnit test runners (one for each \emph{C*}
configuration), reflecting the effects of parallel configurations from
Maven Surefire.  To write those runners we used Maven log files to
identify test classes to run and used the Maven dependency
plugin~\cite{maven-dep} to build the project's classpath with the
command \CodeIn{mvn dependency:build-classpath}. Once we have the
classpath and the tests to run, we invoke our JUnit runner that runs
the test classes with different parallel configurations at once. For
the sequential execution, we invoke the default JUnit test runner. For
parallelism within a JVM (\ie, the configurations \SeqClassParMeth{},
\ParClassSeqMeth{}, and \ParClassParMeth{}), we configured the JUnit
runner with ParallelComputer~\cite{junit-parallel} that internally
uses a pool of threads with cache to run test classes and methods. For
the configurations with forked JVMs (\ie, \ForkSeq{} and
\ForkParMeth{}), we have a queue of test classes and a pool of three
threads that ``consumes'' the next test class and spawns a JVM to run
it.  Recall that in our setup (see Section~\ref{sec:setup}), we
limited our kernel to use only three cores and reserved one for
OS-related processes.  To verify that our approach satisfies the
purpose of this experiment, we executed some subjects on Maven and
compared the performance with our artifacts and observed
insignificant differences (a fraction of seconds in most cases).  To
assure that our experiments terminate (recall that deadlock or livelock
could occur) we used the \CodeIn{timeout} command~\cite{timeout-cmd}
configured to dispatch a \emph{kill} signal if test execution exceeds
a given time limit. Finally, we saved each execution log and stack
traces generated from JUnit to collect the execution time,
the number of failing tests, and for reference to analyze and diagnose
outliers in our results.

>>>>

This experiment evaluates the impact of making a growing number of
CPUs for testing available to the build system.  For that reason, we
used a machine with more cores compared to the one described in
Section~\ref{sec:setup}.  We used a Xeon E5-2660v2 (2.20GHz) Intel
processor machine with 80 virtual CPUs (40 cores with two native
threads each) and 256GB of memory, running Ubuntu 14.04 LTS Trusty
Tahr (64-bit version). This experiment uses configuration
\emph{\ForkSeq{}} as the goal is to evaluate the impact on runtime of
\begin{wrapfigure}{r}[0pt]{0pt}%0.525\linewidth  
  %\begin{figure}[h]
  \centering
  \includegraphics[width=.25\textwidth]{R/scalability/scalability.pdf}
  \caption{\label{fig:scalability}Scalability.}
  %\end{figure}
%  \vspace{-1ex}    
\end{wrapfigure}
spawning a growing number of JVMs in different CPUs.  We selected
subject \subjectScalability{} in this experiment as it represents the
case of a long-running test suite (see Figure~\ref{tab:speedup}) with
test cases distributed across many test classes~--~194.  Note that a
test class is the smallest unit that can be used to spawn a test job
on a JVM and that we have no control over which test classes will be
assigned to which JVM that the build system forks.

@@

It is worth mentioning that we used custom JUnit runners as opposed to
Maven to run \Comment{configurations \emph{C*}}test suites with
different parallel configurations (see Section~\ref{sec:modes}).
After carefully checking library versions for compatibility issues and
comparing results with JUnit's we observed that several of Maven's
executions exposed problems.  For example, Maven incorrectly counts
the number of test cases executed for some cases where test flakiness
are observed.  These issues are categorized and documented on our
website~\cite{ourwebpage} with Docker containers (for reproduction).
To address those issues we implemented basic JUnit test runners (one
for each parallel configuration), reflecting the effects of parallel
configurations from Maven Surefire.  To write those runners we used
Maven log files to identify test classes to run and used the Maven
dependency plugin~\cite{maven-dep} to build the project's classpath
with the command \CodeIn{mvn dependency:build-classpath}. Once we have
the classpath and the tests to run, we invoke our JUnit runner that
runs the test classes with different parallel configurations at
once. For the sequential execution, we invoke the default JUnit test
runner. For parallelism within a JVM (\ie, the configurations
\SeqClassParMeth{}, \ParClassSeqMeth{}, and \ParClassParMeth{}), we
configured the JUnit runner with
ParallelComputer~\cite{junit-parallel} that internally uses a pool of
threads with cache to run test classes and methods. For the
configurations with forked JVMs (\ie, \ForkSeq{} and \ForkParMeth{}),
we have a queue of test classes and a pool of three threads that
``consumes'' the next test class and spawns a JVM to run it.  Recall
that in our setup (see Section~\ref{sec:setup}), we limited our kernel
to use only three cores and reserved one for OS-related processes.  To
verify that our approach satisfies the purpose of this experiment, we
executed some subjects on Maven and compared the performance with our
artifacts and observed insignificant differences (a fraction of
seconds in most cases).  To assure that our experiments terminate
(recall that deadlock or livelock could occur) we used the
\CodeIn{timeout} command~\cite{timeout-cmd} configured to dispatch a
\emph{kill} signal if test execution exceeds a given time
limit. Finally, we saved each execution log and stack traces generated
from JUnit to collect the execution time, the number of failing tests,
and for reference to analyze and diagnose outliers in our results.
